\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage[hidelinks, colorlinks=true, linkcolor=blue, urlcolor=blue]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\hypersetup{
  pdftitle={Salih Bora Öztürk's Resume},
  pdfauthor={Salih Bora Öztürk},
  pdfkeywords={Salih Bora Öztürk, cv, resume, computer, engineer},
}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-3pt}}

\begin{document}

\begin{center}
  \textbf{\Huge \scshape Salih \underline{Bora} Öztürk} \\ \vspace{8pt}
  \small
  \href{https://salihboraozturk.com}{salihboraozturk.com}  $|$
  \href{https://github.com/borawhocodess}{github.com/borawhocodess} $|$
  \href{mailto:boraozturksalih@gmail.com}{boraozturksalih@gmail.com}
\end{center}


\section{Education}
  \resumeSubHeadingListStart

    \resumeSubheading
      {University of Freiburg (Albert-Ludwigs-Universität Freiburg)}{Oct. 2024 -- Present}
      {M.Sc. in Computer Science}{Freiburg, Germany}
      \resumeItemListStart
        \resumeItem{Specializing in Artificial Intelligence with a focus on Tabular Data}
      \resumeItemListEnd

  \resumeSubheading
    {Istanbul Technical University}{Sept. 2019 -- July 2024}
    {B.Sc. in Computer Engineering}{Istanbul, Türkiye}
    \resumeItemListStart
      \resumeItem{GPA: \textbf{3.39}/4  \href{https://web.itu.edu.tr/ozturks19/docs/sbotranscript.pdf}{transcript.pdf}}
      \resumeItem{President of the Student Council, Student Representative of Faculty and Department}
      \resumeItem{ITU ACM Student Chapter, ITU AI Club, ITU Track \& Field, ITU Sailing}
    \resumeItemListEnd

  \resumeSubheading
    {Kaunas University of Technology}{Jan. 2022 -- July 2022}
    {Erasmus+ KA103}{Kaunas, Lithuania}

  \resumeSubheading
    {Kadir Has Anatolian High School}{Sept. 2015 -- June 2019}
    {Mathematics and Sciences}{Istanbul, Türkiye}
    \resumeItemListStart
      \resumeItem{YKS 2019 Rank: \textbf{1686\textsuperscript{th}} \href{https://web.itu.edu.tr/ozturks19/docs/sboyks19.pdf}{yks19.pdf}}
      \resumeItem{Inter-school EYPs, MUNs, Math Olympics, Chess}
    \resumeItemListEnd

  \resumeSubheading
    {Bathurst High School}{Sept. 2016 -- July 2017}
    {ISE WORLD Exchange Program}{New Brunswick, Canada}

  \resumeSubHeadingListEnd


\section{Projects}
  \resumeSubHeadingListStart

  \resumeProjectHeading
      {\textbf{modded-nanoTabPFN} \href{https://github.com/borawhocodess/modded-nanotabpfn}{GitHub}}{Oct. 2024 -- Present}
      \resumeItemListStart
        \resumeItem{Searching for the fastest way to train nanoTabPFN that beats Random Forest on TabArena.}
      \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Threew (Three Words per day)} \href{https://apps.apple.com/app/threew/id6744202891}{AppStore}}{Apr. 2025 -- Present}
    \resumeItemListStart
      \resumeItem{A utility application for tracking the German phrases I learn}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{FFFF (For Friends From Friends)} \href{https://forfriendsfromfriends.com}{forfriendsfromfriends.com}}{Oct. 2023 -- Present}
    \resumeItemListStart
      \resumeItem{A novel social journaling app, graduation project, ranked \textbf{2\textsuperscript{nd}}}
      \resumeItem{Co-developed with M. Eren Cantemür, supervised by Asst. Prof. Gökhan Seçinti}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
    {SDx and Automation Intern}{Dec. 2023 -- Sept. 2024}
    {BTS Group / BTS LABS}{Istanbul, Türkiye}
    \resumeItemListStart
      \resumeItem{Mental Arts Program Graduate}
      \resumeItem{Training in networking, containerization, Linux, CI/CD \& DevOps.}
      \resumeItem{Developed a mobile app, back-end, and Containerlab environment for \\
      configuration retrieval and updates leveraging YANG and NETCONF}
    \resumeItemListEnd

  \resumeSubheading
    {iOS Development Intern}{July 2023 -- Aug. 2023}
    {VSight}{Istanbul, Türkiye}
    \resumeItemListStart
      \resumeItem{Built a demo AR app for the new Apple Vision Pro running on visionOS}
    \resumeItemListEnd


  \resumeSubheading
    {Student Assistant}{Apr. 2021 -- Dec. 2021}
    {ITU IT Department}{Istanbul, Türkiye}
    \resumeItemListStart
      \resumeItem{Provided technical support to ITU users}
      \resumeItem{Obtained CCNA 1 certification}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


\section{Volunteering}
  \resumeSubHeadingListStart

  \resumeSubheading
    {Mentor}{Oct. 2026 -- Present}
    {Intercultural Mentoring Program}{Freiburg, Germany}
    \resumeItemListStart
      \resumeItem{Guiding an international student in adapting to a new life.}
    \resumeItemListEnd

  \resumeSubheading
    {Event Coordinator}{Sept. 2021 -- Jan. 2022}
    {ITU ACM Student Chapter \& ITU AI Club}{Istanbul, Türkiye}
    \resumeItemListStart
      \resumeItem{Organized events and delivered keynotes at “COMP101”}
    \resumeItemListEnd

  \resumeSubheading
    {Lecturer}{Sept. 2019 -- Mar. 2020}
    {ITU Volunteering Club, BBY}{Istanbul, Türkiye}
    \resumeItemListStart
      \resumeItem{Taught high-school-level Geometry and Mathematics}
      \resumeItem{Conducted interviews to select the program-fit candidates}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Technical Skills}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{
      \item{
        Python, PyTorch, C++, Swift, SwiftUI, PyTorch, SQL, SPARQL, HTML/CSS, Git, Docker, VS Code, Xcode
      }
    }
  \end{itemize}

\section{Additional Skills}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{
      \item{
        \textbf{Languages}{: Turkish(Native), English(C1)(IELTS 7.5 \href{https://web.itu.edu.tr/ozturks19/docs/sboielts.pdf}{ielts.pdf}), German(A2)}
        \vspace{4pt} \\
        \textbf{Sports}{: Swimming(Professional, 7 yrs.), Football(Soccer), Basketball, Tennis, Table-tennis, Archery, Sailing, Chess}
        \vspace{4pt} \\
        \textbf{Theatre}{: Müjdat Gezen Sanat Merkezi(2 yrs.), Hasan Ali Yücel Kültür Merkezi(2 yrs.), Kartal Sanat Tiyatrosu(2 yrs.)}
      }
    }
  \end{itemize}

\vspace{30pt}
\begin{center}
  \textit{Phone number and professional references available upon request}
\end{center}

\vspace{25pt}
\begin{flushright}
  \textit{Last updated: January 2025}
  \hspace{20pt}
\end{flushright}

\vfill

\section{Abbreviations}

\begin{itemize}[leftmargin=0.15in, label={}]
    \small{
      \item{
        \textbf{ACM}{: Association for Computing Machinery}
        \vspace{4pt} \\
        \textbf{BBY}{: Bir Başka Yol}
        \vspace{4pt} \\
        \textbf{CCNA}{: Cisco Certified Network Associate}
        \vspace{4pt} \\
        \textbf{EYP}{: European Youth Parliament}
        \vspace{4pt} \\
        \textbf{IELTS}{: International English Language Testing System}
        \vspace{4pt} \\
        \textbf{ITU}{: Istanbul Technical University}
        \vspace{4pt} \\
        \textbf{MUN}{: Model United Nations}
        \vspace{4pt} \\
        \textbf{YKS}{: Yükseköğretim Kurumları Sınavı (Türkiye’s National University Entrance Exam)}
      }
    }
  \end{itemize}

\end{document}

